\documentclass[]{res}

\begin{document}

\namesection{Tianyi (Sam)}{Zhou}{
    \urlstyle{same}\url{https://developersam.com} |
    \href{mailto:tz66@cornell.edu}{tz66@cornell.edu} |
    (607)-279-3876 |
    GitHub: \href{https://github.com/SamChou19815}{\custombold{SamChou19815}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\sectionsep

\runsubsection{Facebook Canada, Ltd}
\descript{| Software Engineer }
\location{January 2025 -- Present | Toronto}
\begin{tightemize}
    \item Implemented various IDE features for \href{https://pyrefly.org}{Pyrefly} from scratch, including autocomplete, find references, and workspace symbol search.
    \item Continuously optimized the type checker and language server performance.
\end{tightemize}
\sectionsep

\runsubsection{Meta}
\descript{| Software Engineer }
\location{February 2022 -- January 2025 | Menlo Park, CA}
\begin{tightemize}
    \item Designed, implemented and deployed the local type inference algorithm based on an improved extension of the \href{https://www.cis.upenn.edu/~bcpierce/papers/lti-toplas.pdf}{Pierce paper} for \href{https://flow.org}{Flow}.
    \item Continuously optimized the type checker and language server performance.
\end{tightemize}
\sectionsep

\runsubsection{Facebook}
\descript{| Software Engineer Intern }
\location{June 2021 -- Aug 2021 | Menlo Park, CA (Remote)}
\begin{tightemize}
    \item Designed and implemented extract to functions/methods/constants/class fields/type aliases refactor code action for Flow's language server. Released to 100\% of Facebook engineers and open source users.
    \item Implemented type checking support for JavaScript private class methods.
\end{tightemize}
\sectionsep

\runsubsection{Facebook}
\descript{| Software Engineer Intern }
\location{June 2020 -- Aug 2020 | Ithaca, NY (Remote)}
\begin{tightemize}
    \item Migrated legacy Java code for Facebook Lite into a new internal framework. Built news feed internal tools for debugging production issues.
    \item Ported election integrity modules to Facebook Lite, increasing global coverage by 20\%.
\end{tightemize}
\sectionsep

\runsubsection{Facebook}
\descript{| Software Engineer Intern }
\location{May 2019 -- Aug 2019 | Menlo Park, CA}
\begin{tightemize}
    \item Designed and implemented an alternative build system that speeds up Python dependency building by 10x.
    \item Implemented Python auto-completion for Pyre language service. Fixed several parsing and type checking bugs.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\sectionsep

\runsubsection{samlang}
\descript{| Rust }
\location{December 2018 -- Present}
\begin{tightemize}
    \item An optimizing source-to-WASM compiler for a functional programming language with generics, first-class functions, type inference, Kotlin-like syntax and OCaml-like semantics.
    \item Includes a language server powering VSCode extension features: type query, auto-completion, and auto-formatting.
\end{tightemize}
\sectionsep

\runsubsection{mini-react}
\descript{| TypeScript }
\location{April 2020}
\begin{tightemize}
    \item A simplified React runtime with support for \texttt{useState} and \texttt{useEffect} hooks.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\sectionsep

\location{Languages}
Rust \textbullet{} Kotlin \textbullet{} Java \textbullet{} OCaml \textbullet{} JavaScript \textbullet{} Hacklang \textbullet{} Python \textbullet{} PHP \textbullet{} Swift \textbullet{} Go \textbullet{} Coq \textbullet{} \LaTeX \\
\location{DevOps}
GitHub Actions \textbullet{} Circle CI \textbullet{} Kubernetes
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\sectionsep

\runsubsection{Cornell University}
\descript{| M.Eng in Computer Science}
\location{Dec 2021 | Ithaca, NY | College of Engineering, Dean's List}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPEN SOURCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Open Source Contributions}

\sectionsep

\href{https://github.com/facebook/docusaurus}{\custombold{facebook/docusaurus}} \textbullet{}
\href{https://github.com/facebook/flow}{\custombold{facebook/flow}} \textbullet{}
\href{https://github.com/facebook/react}{\custombold{facebook/react}} \textbullet{}
\href{https://github.com/facebook/jest}{\custombold{facebook/jest}} \textbullet{}
\href{https://github.com/facebook/pyre-check}{\custombold{facebook/pyre-check}} \textbullet{}
\href{https://github.com/yarnpkg/berry}{\custombold{yarnpkg/berry}}

\end{document}
